Improved Approximation Algorithms for the Maximum Carpool Matching Problme

### 2016-12-19 src/group.tex
group

In this section we introduce the group carpool and show that it does not fit the
submodular maximization formulation.
We show, however, that the problem still has a 
$\frac{1}{2} - \varepsilon$-approximation algorithm.
Finally, we argue that the local search algorithm can be trivially generalized
to handle the new variant of the problem while keeping the same approximation
guarantees.

We start by giving an example why the maximum \textsc{group carpool} problem can
not be formalized as an unconstrained submodular maximization problem as
before.
Considered the instance given in Figure~\ref{fig:not submodular}

>>>>

We now consider a variant of the problem when, in addition to the capacity
function $c:V \to \N$, and the weight (profit) function $w:A \to \R$, we also
have a size function $s:A \to \N$, and the constraint $\din[M] \leq c(v)$
is replaced with the constraint $\sum_{(u,v)}s(u,v) \leq c(v)$.
The motivation for this variant of the problem is when we want to allow a group
of people to travel together in the same car, thus $s$ is the size of the group.

We start by showing that this variant of the problem does not
fit the submodular maximization formulation anymore.
We show, however, that the problem still has a 
$\frac{1}{2} - \varepsilon$-approximation algorithm.
Finally, we argue that the local search algorithm can be trivially generalized
to handle the new variant of the problem while keeping the same approximation
guarantees.

To see why the group carpool problem can not be treated as a
submodular maximization problem considered the instance given in
Figure~\ref{fig:not submodular}.
